Improved Bounds for Online Balanced Repartitioning

### 2020-03-28 paper/paper.tex
Reduction not a LB

  Fix any $k$. If there exists a $\gamma$-competitive deterministic algorithm $B$ for Dynamic Bisection Problem with cluster size $k$, then there exists a $\gamma$-competitive deterministic algorithm $P$ for the paging problem with cache size $2k-1$ and where the number of different pages is $2k$. 
\end{theorem}

\begin{proof}
We partition nodes into $3$ sets $A$, $B$, and $C$.
Sets have cardinalities $|A| = k-1$, $|B| = k-1$, and $|C| = 2$.
Each element $e$ of the universe $U$ have a corresponding node $v_e \in A\cup B\cup C$.
\maciek{define that A,B,C is collocated/split}

>>>>

  Fix any $k$. If there exists a $\gamma$-competitive deterministic algorithm $B$ for Dynamic Bisection Problem with cluster size $k$, then there exists a $\gamma$-competitive deterministic algorithm $P$ for the paging problem with cache size $2k-2$ and where the number of different pages is $2k-1$. 
\end{theorem}

\begin{proof}
  The pages are denoted by $p_1,p_2,\ldots,p_{2k-1}$. Without loss of generality, we assume that the initial cache is equal to $p_1,p_2,\ldots,p_{k-2}$.
  We fix any input sequence $\sigma^P = (\sigma^P_1, \sigma^P_2, \sigma^P_3, \ldots)$ for the caching problem, where $\sigma^P_t$ denotes the $t$-th accessed page.
  We show how to construct an online algorithm $P$ for the caching problem that proceeds in the following online manner.
  The algorithm internally runs the algorithm~$B$, starting on the initial assignment of nodes to clusters that will be defined below.
  For a requested page $\sigma^P_t$, it creates a subsequence of~communication requests for the BRP problem, runs $B$ on them, and serves $\sigma^P_t$ on the basis of $B$'s responses.

  We use $2k$ nodes for the BRP problem: $2k-1$ caching nodes denoted $p_1,p_2, \ldots, p_{2k-1}$, and an auxiliary node $a$.
  We partition nodes into sets $A = \{ a, p_1 \}$, $B = \{ p_2, p_3, \ldots, p_{k+1}\}$, and $C = \{ p_{k+2}, p_{k+3} \ldots, p_{2k-1}\}$.
  Their cardinalities are $|A| = 2$ and $|B| = |C| = k-1$.

  We say that the node configuration is \emph{well-aligned} if any of the following conditions hold:
  \begin{enumerate}
    \item One cluster contains $B$ and one node from $A$ and the other cluster contains $C$ and the other node from $A$.
    \item One cluster contains $B$ and one node from $C$ and the other cluster contains $A$ and $k-2$ nodes from set $C$.
    \item (symmetric to the previous condition) One cluster contains $C$ and one node from $B$ and the other cluster contains $A$ and $k-2$ nodes from set $B$.
  \end{enumerate}
  We show a bijection between cache contents and well-aligned configurations.
  We say that a caching node $p_i \in S$, where $S \in \{ A, B, C\}$ belongs to the cache, if the entire set $S$ is collocated in a cluster.
  Otherwise, if $S$ is split

  one cluster
contains the node $s$ and $k-1$ caching nodes, and the other cluster contains
one caching node and all auxiliary nodes. There is a natural bijection between
possible cache contents and well-aligned configurations: the cache consists of
the $k-1$ caching nodes that are in the same cluster as node $s$. (Without loss
of generality, we may assume that the cache of any caching algorithm is always
full, i.e., consists of $k-1$ pages.) If the configuration $c$ of a~BRP
algorithm is well-aligned, $\textsc{cache}(c)$ denotes the corresponding cache
contents.
The initial configuration for the BRP problem is the well-aligned
configuration corresponding to the initial cache (pages
$p_1,p_2,\ldots,p_{k-1}$ in the cache).

We partition nodes into $3$ sets $A$, $B$, and $C$.
Sets have cardinalities $|A| = k-1$, $|B| = k-1$, and $|C| = 2$.
Each element $e$ of the universe $U$ have a corresponding node $v_e \in A\cup B\cup C$.
\maciek{define that A,B,C is collocated/split}
